An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-26 scagnostics.Rmd
Updated text accordingly.

>>>>

## Summary

Our results can be summarised by evaluating and comparing the advantages and disadvanteges of each index function according to the criteria presented above. An overview is given in Table \ref{tab:summary}. The first three entries are from the scagnostics family. The advantages are good scaling of computing time with sample size and that the set of index functions covers general signatures (the same is however not true for each single index viewed on its own). On the other hand we have found that they are typically too noisy making optimisation of the function challenging. In particular the stringy index cannot be used with current optimisers. The index functions from @mbgraphic share similar behaviour as they are both found to evolve fairly smoothly between interpolated projections, but have been shown to be strongly rotation dependent. The splines2D index is fast to calculate and found to be the most efficient method for identifying functional dependence. We have only considered the non-binned implementation of dcor2D which is slow to calculate on large datasets. While this index is in principle general, we have found it to be too sensitive to noise to be applicable in most realistic examples. Finally the MINE indexes are found to be smooth only for large datasets, with some rotation dependence observed for the TIC index. While these indexes are slow to compute especially on large datasets, we have found them to be the most general, allowing good discrimination even with noisy structures.

\begin{table}
\begin{center}
\caption{Summary}
\label{tab:summary}
\begin{tabular}{|l|c|c|c|c|}
\hline
Index & smooth & rotation invariant & fast & general \\
\hline
Convex & ! & ! & \checkmark & ! \\
Skinny & ! & ! & \checkmark & ! \\
Stringy & $\times$ & ! & \checkmark & ! \\
\hline
splines2D & \checkmark & $\times$ & \checkmark & ! \\
dcor2D & \checkmark & $\times$ & ! & ! \\
\hline
MINE & ! & ! & ! & \checkmark\\
\hline
\end{tabular}
\end{center}
\end{table}
